Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-15 WSSSPE1_report/WSSSPE1_summary_report.tex
Eliminate a title in affliction.
Eliminate street in affliction.

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}
%
\thanks{{}$^{(3)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(4)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(5)}$ Center for Computation and Technology, Louisiana State University, Baton Rouge, LA, USA; \url{knarf@cct.lsu.edu}}
%
\thanks{{}$^{(6)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ Scientific Computing Group, Kitware, Inc., 28 Corporate Drive, Clifton Park, NY, USA; \url{marcus.hanwell@kitware.com}}
%
\thanks{{}$^{(8)}$ San Diego Supercomputer Center, University of California San Diego, La Jolla, CA, USA, \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(9)}$ Leader, Research Software Development Team, University College London, London, UK; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(10)}$ University of Texas at Austin, Austin, TX, USA; \url{jhowison@ischool.utexas.edu}}
% 
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}

>>>>

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and   Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}
%
\thanks{{}$^{(3)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(4)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(5)}$ Center for Computation and Technology, Louisiana State University, Baton Rouge, LA, USA; \url{knarf@cct.lsu.edu}}
%
\thanks{{}$^{(6)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ Scientific Computing Group, Kitware, Inc.,  Clifton Park, NY, USA; \url{marcus.hanwell@kitware.com}}
%
\thanks{{}$^{(8)}$ San Diego Supercomputer Center, University of California San Diego, La Jolla, CA, USA, \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(9)}$ Research Software Development Team, University College London, London, UK; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(10)}$ University of Texas at Austin, Austin, TX, USA; \url{jhowison@ischool.utexas.edu}}
% 
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}
